Sleep, relative to wake, increases both veridical and false memory in the DRM paradigm:

### 2023-07-11 manuscript.Rmd
Removed activation of LSAfun
Moved LSAfun out of the list to activate

@@

``` {r activate2}

install.packages("LSAfun")
library(LSAfun)

@@

my_list <- vector()
for (i in 1:length(intrusion_item)){
  new_element <- Cosine(lure_item[1], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[2], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[3], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[4], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[5], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[6], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[7], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[8], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[9], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[10], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[11], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[12], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[13], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[14], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[15], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[16], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[17], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[18], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[19], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- Cosine(lure_item[20], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  }

>>>>

# currently activating the LSA package seems to crash the script on github
# now trying a direct call to the Cosine function with the package unactivated

# install.packages("LSAfun")

@@

@@

my_list <- vector()
for (i in 1:length(intrusion_item)){
  new_element <- LSAfun::Cosine(lure_item[1], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[2], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[3], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[4], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[5], intrusion_item[i], ukwac)
  my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[6], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[7], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[8], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[9], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[10], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[11], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[12], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[13], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[14], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[15], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[16], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[17], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[18], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[19], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  new_element <- LSAfun::Cosine(lure_item[20], intrusion_item[i], ukwac)
   my_list[[length(my_list) + 1]] <- new_element
  }
